---
title: "XL's_presentation"
author: "Xiang Li"
date: "10/8/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("XL's_wrangling_Code.R")
source("XL's_visualization_function.R")
```

## Overview
- Datasets chosen: From https://www.gapminder.org/data/
- Two indicators in two datasets: Babies per women(total fertility)
                             - & Employment rate(%), females aged 15+
- Country chosen: Top Five Fastest Developing Countries 
      from https://borgenproject.org/top-5-fastest-developing-countries/
    - which are Argentina, India , China, Brazil, Guyana
                 - Five Developed Countries
    - which are United States, France, United Kingdom, Belgium, Spain

## Developed Countries: Fertility   
- (United States, France, United Kingdom, Belgium, Spain)

```{r}
visualization_function(data_join, country1 = "United States", country2 = "France",country3 = "United Kingdom", country4="Belgium",country5="Spain", indicators  = "fertility")
```

## Developed Countries: Employment% 
- (United States, France, United Kingdom, Belgium, Spain)

```{r}
visualization_function(data_join, country1 = "United States", country2 = "France",country3 = "United Kingdom",country4="Belgium",country5="Spain", indicators = "femployrate")
```

## Developing Countries: Fertility
- (Argentina, India , china, Brazil, guyana)
```{r}
visualization_function(data_join, country1 = "Argentina", country2 = "India",country3 = "China", country4="Brazil",country5="Guyana", indicators  = "fertility")

```

## Developing Countries: Employment%  
- (Argentina, India , china, Brazil, guyana)
```{r}
visualization_function(data_join, country1 = "Argentina", country2 = "India",country3 = "China", country4="Brazil",country5="Guyana", indicators = "femployrate")
```

## Comparison
- Fertility vs Employment Rate in Developed Countries
     - when the Employment Rate is increasing from 1990 to 2020, the fertility is decreasing
  - However,
- Fertility vs Employment Rate in Developing Countries
     - when the Employment Rate and fertility rate are both decreasing from 1990 to 2020.
 
## Thought
- Before I analyzed these two data sets, I think that the employment rate should be increasing no matter in which kinds country, especially, I chose five top fast developing countries in the world.
- Moreover, I used to believe that the fertility rate is decreasing and one of the main reason is that female's employment rate is increasing.
- The employment rates have different trend in developed and developing countries.
